---
title: "DDP_Ex_1"
author: "Igor"
date: "October 10, 2016"
output: ioslides_presentation
---


## My new slide

### A top level subheading 

#### A second level subheading

## Next slide - now full of content

- Bullet 1
- Bullet 2

1. Item 1
2. Item 2

## One more slide - simple formating options

*Italicized text*

**Bold text**

`for(i %in% 1:20)` 

## Running `R` code with the output

```{r}

head(mtcars)

```

## A plot

```{r, echo=FALSE, fig.align='center', fig.cap= "Just a graph"}

plot(y = mtcars$mpg, x = mtcars$wt, ylab = "mgp", xlab = "Car weight" )

```


## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```

